---
title: "Maternal_dx_ASD"
author: "VK"
date: "1/11/2024"
output: html_document
---
###Loading the required libraries used by the code
```{r include=FALSE}
library(tidyverse)
library(readxl)
library(icd.data)
library(fdrtool)
```

```{r}
a <- icd10_sub_chapters
b <- icd10cm2016
colnames(b)
ICD10 <- distinct(b, three_digit, short_desc, major, sub_chapter, chapter) %>% rename(ICD10_3 = three_digit) %>% distinct(ICD10_3, .keep_all = T)
```

```{r setup, include=FALSE}
######****************************
file_path <- "/Users/vk/Library/CloudStorage/OneDrive-Personal/Documents/Mount Sinai/-Projects/4. M_dx_R01/Data/DK_R01_2023_03_22_EA_fix_issues copy.xlsx"

sheet_names <- excel_sheets(file_path)
data_frames <- list()

# Loop through each sheet and read it into a data frame
for (sheet_name in sheet_names) {
  data <- read_excel(file_path, sheet = sheet_name)  # Replace file_path with your file's path or file_url with your URL
  data_frames[[sheet_name]] <- data
}


######**************************
file_path <- "/Users/vk/Library/CloudStorage/OneDrive-Personal/Documents/Mount Sinai/-Projects/4. M_dx_R01/Data/DK_R01_review_2024_05_03.xlsx"
sheet_names <- excel_sheets(file_path)
for (sheet_name in sheet_names) {
  data <- read_excel(file_path, sheet = sheet_name)  # Replace file_path with your file's path or file_url with your URL
  data_frames[[sheet_name]] <- data
}


######**************************
file_path <- "/Users/vk/Library/CloudStorage/OneDrive-Personal/Documents/Mount Sinai/-Projects/4. M_dx_R01/Data/DK_R01_review_2024_05_03b.xlsx"
sheet_names <- excel_sheets(file_path)
for (sheet_name in sheet_names) {
  data <- read_excel(file_path, sheet = sheet_name)  # Replace file_path with your file's path or file_url with your URL
  data_frames[[sheet_name]] <- data
}

# Model 1: Running Cox proportional hazard model to examine the association between diagnoses and ASD -- only birth year
# Model 2: Running Cox proportional hazard model to examine the association between diagnoses and ASD -- Model 1 + sex + mom's age 
# Model 3: Running Cox proportional hazard model to examine the association between diagnoses and ASD -- Model 2 + health care utilization
# Model 4: Running Cox proportional hazard model to examine the association between diagnoses and ASD -- Model 3 + Mom's Edu
# Model 5: Running Cox proportional hazard model to examine the association between diagnoses and ASD -- Model 4 + Mom's Income

# Model 11: all significant acute and chronic conditions + covariates from Model 5
# Model 12: Model 11 + acute conditions from 12-24 months
# Model 13: Model 11 + acute conditions from 24-36 months
# Model 14: Model 11 + acute conditions from 36-48 months
# Model 15: Model 11 + acute conditions from 24-48 months
# Model 16: Model 11 + acute conditions from 12-24, 24-36, and 36-48 months
# Model 11 S1 ref: Model 11 limited to those with paternal income data
# Model 11 S1: Model 11 + paternal income
# Model 11 S2: Model 11 + parity
# Model 11 S3: Model 11 only among those with parity = 1
# Model 11 S4: Model 11 among singletons only
# Model 11 S5: Model 11 among those with mother without ASD dx
# Model 17: individual dx models for all timing windows, i.e. 0-12, 12-24, 24-36, and 36-48 months + covariates from Model 11.
# Model 20: Model 4 with parity and DOBY as factor rather than strata among sibiling sample
# Model 21: sibling analysis of model 11 + parity
# Model 21b: Sibling analysis of model 11 with parity and DOBY as factor rather than strata
# Model 20 S6: Model 20 among male only
# Model 21 S6: Model 21b among male only
# Model 11 S7m: Model 11 among male only
# Model 11S7f: Model 11 among female only
# Model 11 S8id: Model 11 among those with intellectual disability (ID)
# Model 11 S8nid: Model 11 among those without ID
# Model 21c: I did not see this in my code. Perhaps we can check with Elias. 
# Model 21c S6: I did not see this in my code. Perhaps we can check with Elias. 
# Model 4o 5n chronic exp: (Model_05_S5) Model 5 chronic disease with 12/ 48, and 72 months window.
# Model 4o 5n, wo missing fathers: (Model_05_S7) Model 5 without missing father infor
# Model 11 w covariates: (Model11_COV) Model 11 covariates
# Model 4o 5n +1 dx: (Model_05_S6) Model 5 where exposure is defined by at least 2 records rather than 1.
# Model 4o 5n n_diag_0012: (Model05_S1) Model 5 where health care utilization variable is number of diagnosis.
# Model 4o 5n n_visits_0048: (Model05_S2) Model 5 where health care utilization variable days of encounter during 48 months period before child's birth.
# Model 4o 5n wo health: (Model05_S3) Model 5 without health
# Model 4o 5n born before 2010: (Model05_S4) Model 5 among those born before 2010

sheet_names
Model01 <- data_frames[[1]]
Model02 <- data_frames[[29]]
Model03 <- data_frames[[2]]
Model04 <- data_frames[[3]]
Model05 <- data_frames[[4]]
Model11 <- data_frames[[5]]
Model12 <- data_frames[[6]]
Model13 <- data_frames[[7]]
Model14 <- data_frames[[8]]
Model15 <- data_frames[[9]]
Model16 <- data_frames[[10]]
Model11_s1ref <- data_frames[[11]]
Model11_s1 <- data_frames[[12]]
Model11_s2 <- data_frames[[13]]
Model11_s3 <- data_frames[[14]]
Model11_s4 <- data_frames[[15]]
Model11_s5 <- data_frames[[33]]
Model17 <- data_frames[[17]]
Model20 <- data_frames[[30]]
Model21 <- data_frames[[19]]
Model21_b <- data_frames[[31]]
Model20_s6 <- data_frames[[21]]
Model21_s6 <- data_frames[[32]]
Model11_s7m <- data_frames[[23]]
Model11_s7f <- data_frames[[24]]
Model11_s8id <- data_frames[[25]]
Model11_s8nid <- data_frames[[26]]
Model21c_s6 <- data_frames[[27]]
Model21_c <- data_frames[[28]]
Model05_S1 <- data_frames[[42]]
Model05_S2 <- data_frames[[43]]
Model05_S3 <- data_frames[[34]]
Model05_S4 <- data_frames[[35]]
Model05_S5 <- data_frames[[36]]
Model05_S6 <- data_frames[[39]]
Model05_S7 <- data_frames[[37]]
Model11_COV <- data_frames[[38]]

Model17 <- rbind(names(Model17), Model17)

table_asd_dx_A <- data <- read_excel("/Users/vk/Library/CloudStorage/OneDrive-Personal/Documents/Mount Sinai/-Projects/4. M_dx_R01/Data/table1.xlsx", sheet = "Table S1, 0-12")
colnames(table_asd_dx_A) <- c("ICD10_3", "ASD", "No_ASD")

table_asd_dx_C <- data <- read_excel("/Users/vk/Library/CloudStorage/OneDrive-Personal/Documents/Mount Sinai/-Projects/4. M_dx_R01/Data/table1.xlsx", sheet = "Table S2")
colnames(table_asd_dx_C) <- c("ICD10_3", "ASD", "No_ASD")

table_asd_dx <- rbind(table_asd_dx_A, table_asd_dx_C)
pat_mat_04 <- read_excel("/Users/vk/Library/CloudStorage/OneDrive-Personal/Documents/Mount Sinai/-Projects/4. M_dx_R01/Data/paternal_2023_10_04.xlsx", sheet = "model_4") %>% mutate(p_m = substr(ICD10, 1,1), ICD10_3 = substr(ICD10, 3,5)) %>% left_join(ICD10, by = "ICD10_3")
table_prevalence <- table_asd_dx %>%
    mutate(prevalence = ((ASD + No_ASD)/1131899)*100) %>% 
  mutate(prevalence_pct = paste0(format(round(prevalence, digits = 2), nsmall = 2), "%"))
```

```{r formatting_df_q}
formatting_df_q <-  function(df){
df$HRc <- format(round(df$HR,2), nsmall = 2)
df$LL <- format(round(df$`2.5%`,2), nsmall = 2)
df$UL <- format(round(df$`97.5%`,2), nsmall = 2)
df$HR95 <- paste(df$HRc, (paste(df$LL, (paste(df$UL, "]", sep = "")), sep = ", ")), sep = " [")
df$sig <- ifelse(df$`q-val` < 0.05, "*", "")
df$sig <- ifelse(df$`q-val`  < 0.01, "**", df$sig)
df$sig <- ifelse(df$`q-val`  < 0.001, "***", df$sig)
df$HR95 <- paste(df$HR95, df$sig, sep ="")
df$ICD10_3 <- substr(df$ICD10, nchar(df$ICD10)-3+1, nchar(df$ICD10))
df$a_c <- substr(df$ICD10, 1, 5)
df$a_c[df$a_c== "m0012"] <- "A"
df$a_c[df$a_c== "m0048"] <- "C"
df <- left_join(df, ICD10, by = "ICD10_3")
return(df)}

formatting_df_p_2 <-  function(df){
df$HRc <- format(round(df$HR,2), nsmall = 2)
df$LL <- format(round(df$`2.5%`,2), nsmall = 2)
df$UL <- format(round(df$`97.5%`,2), nsmall = 2)
df$HR95 <- paste(df$HRc, (paste(df$LL, (paste(df$UL, "]", sep = "")), sep = ", ")), sep = " [")
df$sig <- ifelse(df$`p-val` < 0.05, "*", "")
df$sig <- ifelse(df$`p-val`  < 0.01, "**", df$sig)
df$sig <- ifelse(df$`p-val`  < 0.001, "***", df$sig)
df$HR95 <- paste(df$HR95, df$sig, sep ="")
df <- df %>% rename(p_val = `p-val`)
df$ICD10_3 <- substr(df$ICD10, nchar(df$ICD10)-3+1, nchar(df$ICD10))
df$a_c <- substr(df$ICD10, 1, 5)
df$a_c[df$a_c== "m0012"] <- "A"
df$a_c[df$a_c== "m0048"] <- "C"
df <- left_join(df, ICD10, by = "ICD10_3")
return(df)}

formatting_df_p <-  function(df){
df <- df %>% rename(HR = exp.coef., `2.5%` = lower..95, `97.5%` = upper..95, ICD10 = ...1)         
df$HRc <- format(round(df$HR,2), nsmall = 2)
df$LL <- format(round(df$`2.5%`,2), nsmall = 2)
df$UL <- format(round(df$`97.5%`,2), nsmall = 2)
df$HR95 <- paste(df$HRc, (paste(df$LL, (paste(df$UL, "]", sep = "")), sep = ", ")), sep = " [")
df$sig <- ifelse(df$p_val < 0.05, "*", "")
df$sig <- ifelse(df$p_val  < 0.01, "**", df$sig)
df$sig <- ifelse(df$p_val  < 0.001, "***", df$sig)
df$HR95 <- paste(df$HR95, df$sig, sep ="")
df$ICD10_3 <- substr(df$ICD10, nchar(df$ICD10)-3+1, nchar(df$ICD10))
df <- left_join(df, ICD10, by = "ICD10_3")
return(df)}
```

```{r}
Model01 <- formatting_df_q(Model01)
Model02 <- formatting_df_q(Model02)
Model03 <- formatting_df_q(Model03)
Model04 <- formatting_df_q(Model04)
Model05 <- formatting_df_q(Model05)
Model11 <- formatting_df_p(Model11)
Model12 <- formatting_df_p(Model12)
Model13 <- formatting_df_p(Model13)
Model14 <- formatting_df_p(Model14)
Model15 <- formatting_df_p(Model15)
Model16 <- formatting_df_p(Model16)
Model11_s1ref <- formatting_df_p(Model11_s1ref)
Model11_s1 <- formatting_df_p(Model11_s1)
Model11_s2 <- formatting_df_p(Model11_s2)
Model11_s3 <- formatting_df_p(Model11_s3)
Model11_s4 <- formatting_df_p(Model11_s4)
Model11_s5 <- formatting_df_p(Model11_s5)
#Model17 <- formatting_df_p(Model17)
Model20 <- formatting_df_p_2(Model20)
Model21 <- formatting_df_p(Model21)
Model21_b <- formatting_df_p_2(Model21_b)
Model20_s6 <- formatting_df_p(Model20_s6)
Model21_s6 <- formatting_df_p_2(Model21_s6)
Model11_s7m <- formatting_df_p(Model11_s7m)
Model11_s7f <- formatting_df_p(Model11_s7f)
Model11_s8id <- formatting_df_p(Model11_s8id)
Model11_s8nid <- formatting_df_p(Model11_s8nid)
Model21c_s6 <- formatting_df_p(Model21c_s6)
Model21_c <- formatting_df_p(Model21_c)

Model05_S1 <- formatting_df_q(Model05_S1)
Model05_S2 <- formatting_df_q(Model05_S2)
Model05_S3 <- formatting_df_q(Model05_S3)
Model05_S4 <- formatting_df_q(Model05_S4)
Model05_S5 <- formatting_df_q(Model05_S5)
Model05_S6 <- formatting_df_q(Model05_S6)
Model05_S7 <- formatting_df_q(Model05_S7)
Model11_COV <- formatting_df_p(Model11_COV)

Model05_S5A <- Model05_S5 %>% 
  filter(a_c == "A") %>% 
  mutate(a_c = "C") %>%
  rbind((Model05 %>% filter(a_c== "A")))

result <- fdrtool(Model05_S5A$`p-val`, statistic = "pvalue")
Model05_S5A$`q-val` <- result$qval

Model05_S5A$HR95 <- gsub("[*]", "", Model05_S5A$HR95)
Model05_S5A$sig <- ifelse(Model05_S5A$`q-val` < 0.05, "*", "")
Model05_S5A$sig <- ifelse(Model05_S5A$`q-val`  < 0.01, "**", Model05_S5A$sig)
Model05_S5A$sig <- ifelse(Model05_S5A$`q-val`  < 0.001, "***", Model05_S5A$sig)
Model05_S5A$HR95 <- paste0(Model05_S5A$HR95, Model05_S5A$sig)

Model05_S5B <- Model05_S5 %>% 
  filter(a_c == "m0072") %>%
  mutate(a_c = "C") %>%
  rbind((Model05 %>% filter(a_c== "A")))

result <- fdrtool(Model05_S5B$`p-val`, statistic = "pvalue")
Model05_S5B$`q-val` <- result$qval

Model05_S5B$HR95 <- gsub("[*]", "", Model05_S5B$HR95)
Model05_S5B$sig <- ifelse(Model05_S5B$`q-val` < 0.05, "*", "")
Model05_S5B$sig <- ifelse(Model05_S5B$`q-val`  < 0.01, "**", Model05_S5B$sig)
Model05_S5B$sig <- ifelse(Model05_S5B$`q-val`  < 0.001, "***", Model05_S5B$sig)
Model05_S5B$HR95 <- paste0(Model05_S5B$HR95, Model05_S5B$sig)


Model05_S5C <- Model05_S5 %>% 
  filter(a_c == "C") %>%
  rbind((Model05 %>% filter(a_c== "A")))

result <- fdrtool(Model05_S5C$`p-val`, statistic = "pvalue")
Model05_S5C$`q-val` <- result$qval

Model05_S5C$HR95 <- gsub("[*]", "", Model05_S5C$HR95)
Model05_S5C$sig <- ifelse(Model05_S5C$`q-val` < 0.05, "*", "")
Model05_S5C$sig <- ifelse(Model05_S5C$`q-val`  < 0.01, "**", Model05_S5C$sig)
Model05_S5C$sig <- ifelse(Model05_S5C$`q-val`  < 0.001, "***", Model05_S5C$sig)
Model05_S5C$HR95 <- paste0(Model05_S5C$HR95, Model05_S5C$sig)


Model05_S6 <- Model05_S6 %>% 
  filter(a_c == "C") %>% 
  rbind((Model05 %>% filter(a_c== "A")))

result <- fdrtool(Model05_S6$`p-val`, statistic = "pvalue")
Model05_S6$`q-val` <- result$qval

Model05_S6$HR95 <- gsub("[*]", "", Model05_S6$HR95)
Model05_S6$sig <- ifelse(Model05_S6$`q-val` < 0.05, "*", "")
Model05_S6$sig <- ifelse(Model05_S6$`q-val`  < 0.01, "**", Model05_S6$sig)
Model05_S6$sig <- ifelse(Model05_S6$`q-val`  < 0.001, "***", Model05_S6$sig)
Model05_S6$HR95 <- paste0(Model05_S6$HR95, Model05_S6$sig)

Model05_sig <- Model05 %>% filter(`q-val` <0.05)
Model01_05 <- Model01 %>% 
  select(ICD10_3, HR95) %>% 
  rename(M01_HR95 = HR95) %>%
  left_join((Model02 %>% 
               select(ICD10_3, HR95) %>% 
               rename(M02_HR95 = HR95)), by = "ICD10_3") %>%
  left_join((Model03 %>%
               select(ICD10_3, HR95) %>%
               rename(M03_HR95 = HR95)), by = "ICD10_3") %>%
  left_join((Model04 %>% 
               select(ICD10_3, HR95) %>% 
               rename(M04_HR95 = HR95)), by = "ICD10_3") %>% 
  left_join((Model05 %>% 
               select(ICD10_3, HR95, major, sub_chapter, chapter, a_c) %>% 
               rename(M05_HR95 = HR95)), by = "ICD10_3") %>% 
        select(ICD10_3, a_c, chapter, sub_chapter, major, M01_HR95, M02_HR95, M03_HR95, M04_HR95, M05_HR95)
a_c <- Model05 %>% select(ICD10_3, a_c)

Model05.11 <-   Model05 %>% 
        select(HR, `2.5%`, `97.5%`, ICD10_3, major, sub_chapter, chapter) %>% mutate(model = "05") %>%
        filter(ICD10_3 %in% Model11$ICD10_3) %>% 
        rbind(Model11 %>% 
        select(HR, `2.5%`, `97.5%`, ICD10_3, major, sub_chapter, chapter) %>% 
                mutate(model = "11")) %>%
        left_join(a_c, by = "ICD10_3")
```

# Sensitivity Models based on model 5
```{r}
Model05_SS <- Model05 %>% 
  left_join((Model05_S1 %>% 
               select(ICD10_3, HR95) %>% 
               rename(S01_HR95 = HR95)), by = "ICD10_3") %>%
  left_join((Model05_S2 %>%
               select(ICD10_3, HR95) %>%
               rename(S02_HR95 = HR95)), by = "ICD10_3") %>%
  left_join((Model05_S3 %>% 
               select(ICD10_3, HR95) %>% 
               rename(S03_HR95 = HR95)), by = "ICD10_3") %>% 
  left_join((Model05_S4 %>% 
               select(ICD10_3, HR95) %>% 
               rename(S04_HR95 = HR95)), by = "ICD10_3") %>%
  left_join((Model05_S5A %>% 
               select(ICD10_3, HR95) %>% 
               rename(S05A_HR95 = HR95)), by = "ICD10_3") %>%
  left_join((Model05_S5B %>% 
               select(ICD10_3, HR95) %>% 
               rename(S05B_HR95 = HR95)), by = "ICD10_3") %>%
  left_join((Model05_S5C %>% 
               select(ICD10_3, HR95) %>% 
               rename(S05C_HR95 = HR95)), by = "ICD10_3") %>% 
  left_join((Model05_S6 %>%
               select(ICD10_3, HR95) %>% 
               rename(S06_HR95 = HR95)), by = "ICD10_3") %>% 
        select(ICD10_3, a_c, chapter, sub_chapter, major, HR95, S01_HR95, S02_HR95, S02_HR95, S03_HR95, S04_HR95, S05A_HR95, S05B_HR95, S05C_HR95, S06_HR95)

Model05_SS_A <- Model05_SS %>% filter(a_c == "A") %>% 
  select(ICD10_3, a_c, chapter, sub_chapter, major, HR95, S01_HR95, S02_HR95, S02_HR95, S03_HR95, S04_HR95)
write_csv(Model05_SS_A, "Tables/TabS03_Model05_SS_A.csv")

Model05_SS_C <- Model05_SS %>% filter(a_c == "C")
write_csv(Model05_SS_C, "Tables/TabS04_Model05_SS_C.csv")
```

# Saving Covarites of Model 11
```{r}

Model11_COV <- Model11_COV %>% 
  filter(is.na(major))
write_csv(Model11_COV, "Tables/TabS05_Covariates.csv")
```


# Figure 01A Manhattan plot for model 5
```{r}
Model05 <- Model05[order(Model05$chapter),]
Model05 <- Model05 %>% mutate(ICD10_1 = as.integer(factor(chapter)))
Model05$num <- 1:nrow(Model05)+1
Model05$`p-val`[Model05$`p-val` < 2e-30] <- 2e-30
Model05$p <- -log(Model05$`p-val`)

palette <- c("#394165", "#48211A", "#78A8D1", "#376597", "#A13826", "#537270",  "#556246", "#928F6B", "#CCAF69", "#9dd6d6", "#104A8A", "#C5AC8E", "#889F95", "#7C4728", "cadetblue4", "#00295D", "#D9B196", "#B1934A")

## all diagnoses, scatterplot, significance, by ICD-9 level 1 

plot <- ggplot(Model05, aes(x=num, y=p)) + 
  geom_point(aes(col=chapter, size=HR)) + 
  ylim(c(0, 63)) + 
  scale_colour_manual(values = palette) + 
  geom_hline(yintercept=2.995732) +
  geom_hline(yintercept=4.767689) +
  scale_x_discrete(name ="", breaks=NULL) + 
  theme(legend.title = element_text(size = 5), 
  legend.text = element_text(size = 5)) + 
  theme_bw() + 
      labs(subtitle="All diagnoses", 
       y="-log(p)", 
       x="ICD10 codes", 
       title="Association of maternal diagnoses with offspring ASD", 
       caption = "") +
  guides(color = guide_legend(title = "ICD-10 Dx categories"), size = guide_legend(title = "Hazard ratio"))


ggsave("Figures/Fig_01A_Model05_all.png", plot, width = 14, height = 7)
```


# Figure 01B Volcano plot for model 5
```{r}
Model05 <- Model05[order(Model05$chapter),]
Model05 <- Model05 %>% mutate(ICD10_1 = as.integer(factor(chapter)))
Model05$num <- 1:nrow(Model05)+1
Model05$`p-val`[Model05$`p-val` < 2e-30] <- 2e-30
Model05$p <- -log(Model05$`p-val`)
Model05_volc <- Model05
Model05_volc$log_hr <- log(Model05_volc$HR)
Model05_volc$sig_chapter <- ifelse(Model05_volc$sig == "", "P-value not significant (FDR-adjusted)", as.character(Model05_volc$chapter))
Model05_volc$sig_chapter <- factor(Model05_volc$sig_chapter, levels = c("Diseases of the circulatory system", 
                                                                        "Diseases of the genitourinary system",
                                                                        "Diseases of the musculoskeletal system and connective tissue", 
                                                                        "Diseases of the nervous system", 
                                                                        "Diseases of the respiratory system",
                                                                        "Endocrine, nutritional and metabolic diseases",
                                                                        "Factors influencing health status and contact with health services",
                                                                        "Injury, poisoning and certain other consequences of external causes",
                                                                        "Mental, Behavioral and Neurodevelopmental disorders",
                                                                        "Neoplasms",
                                                                        "Pregnancy, childbirth and the puerperium",
                                                                        "P-value not significant (FDR-adjusted)"))
table(Model05_volc$sig_chapter)

Model05_volc$label <- ifelse(Model05_volc$sig == "", NA, as.character(Model05_volc$major))

plot <- ggplot(data = Model05_volc, aes(x = HR, y = -log10(`p-val`), col = sig_chapter, #label = label 
      )) +
  scale_x_continuous(trans = 'log', breaks = c(0.50, 0.66, 1.00, 1.50, 2.00, 3.00)) +
  geom_vline(xintercept = c(1), col = "black", linetype = 'dashed') +
  geom_hline(yintercept = -log10(0.05), col = "black", linetype = 'dashed') +
  geom_point(size = 2) + scale_color_manual(values = c("#9dd6d6", "#48211A", "#78A8D1", "#376597", "#C5AC8E", "#537270",  "#556246", "#928F6B", "#00295D", "#9dd6d6", "#A13826", "grey")) + 
  # theme(legend.position = "bottom") + 
  labs(subtitle="All diagnoses", 
       y="-log10(p)", 
       x="HR", 
       title="Association of maternal diagnoses with offspring ASD", 
       caption = "") +
  guides(color = guide_legend(title = "ICD-10 Dx categories"))  + 
  theme(legend.title = element_text(size = 6),
  legend.text = element_text(size = 8)) + 
  theme_bw() +
  theme(axis.text = element_text(size = 14),
        axis.title=element_text(size=14,face="bold"))

ggsave("Figures/Fig_01B_Model05_all.png", plot, width = 14, height = 7)

plot <- ggplot(data = Model05_volc, aes(x = log_hr, y = -log10(`p-val`), col = sig_chapter, label = label 
                                )) +
  geom_vline(xintercept = c(0), col = "black", linetype = 'dashed') +
  geom_hline(yintercept = -log10(0.05), col = "black", linetype = 'dashed') +
  geom_point(size = 2) + scale_color_manual(values = c("#9dd6d6", "#48211A", "#78A8D1", "#376597", "#C5AC8E", "#537270",  "#556246", "#928F6B", "#00295D", "#9dd6d6", "#A13826", "grey")) + 
  # theme(legend.position = "bottom") + 
  labs(subtitle="All diagnoses", 
       y="-log10(p)", 
       x="log HR", 
       title="Association of maternal diagnoses with offspring ASD", 
       caption = "") +
  guides(color = guide_legend(title = "ICD-10 Dx categories")) +
# Plot title 
  ggrepel::geom_text_repel(max.overlaps = Inf, force_pull   = 0, # do not pull toward data points
    nudge_y      = 0.05,
    direction    = "x",
    angle        = 90,
    hjust        = 0,
    segment.size = 0.2) + 
  theme(legend.title = element_text(size = 5),
  axis.text = element_text(size = 10),
  legend.text = element_text(size = 5)) + 
  theme_bw()

ggsave("Figures/Fig_01C_Model05_all.png", plot, width = 14, height = 7)


plot <- ggplot(data = Model05_volc, aes(x = HR, y = -log10(`p-val`), col = sig_chapter, #label = label 
      )) +
  scale_x_continuous(trans = 'log', breaks = c(0.50, 0.66, 1.00, 1.50, 2.00, 3.00)) +
  geom_vline(xintercept = c(1), col = "black", linetype = 'dashed') +
  geom_hline(yintercept = -log10(0.05), col = "black", linetype = 'dashed') +
  geom_point(size = 1.8) + scale_color_manual(values = c("#9dd6d6", "#48211A", "#78A8D1", "#376597", "#C5AC8E", "#537270",  "#556246", "#928F6B", "#00295D", "#9dd6d6", "#A13826", "grey")) + 
  # theme(legend.position = "bottom") + 
  labs(subtitle="All diagnoses", 
       y="-log10(p)", 
       x="HR", 
       title="Association of maternal diagnoses with offspring ASD", 
       caption = "") + theme_bw() +
  theme(legend.position = "none") +
  theme(axis.text = element_text(size = 10))
ggsave("Figures/Fig_01B_Model05_all_nolegend.png", plot, width = 5, height = 4)
```


```{r}
# (values = c("#394165", "#48211A", "#78A8D1", "#376597", "#A13826", "#537270",  "#556246", "#928F6B", "#CCAF69", "#9dd6d6", "grey", "#C5AC8E"))
```


```{r}
# palette <- c("#394165", "#48211A", "#78A8D1", "#376597", "#A13826", "#537270",  "#556246", "#928F6B", "#CCAF69", "#9dd6d6", "#104A8A", "#C5AC8E", "#889F95", "#7C4728", "cadetblue4", "#00295D", "#D9B196", "#B1934A")
# 
# ## all diagnoses, scatterplot, significance, by ICD-9 level 1 
# 
# plot <- ggplot(Model05, aes(x=num, y=p)) + 
#   geom_point(aes(col=chapter, size=HR)) + 
#   ylim(c(0, 63)) + 
#   scale_colour_manual(values = palette) + 
#   geom_hline(yintercept=2.995732) +
#   geom_hline(yintercept=4.767689) +
#   scale_x_discrete(name ="", breaks=NULL) + 
#   theme(legend.title = element_text(size = 5), 
#   legend.text = element_text(size = 5)) + 
#   theme_bw() + 
#       labs(subtitle="All diagnoses", 
#        y="-log(p)", 
#        x="ICD10 codes", 
#        title="Association of maternal diagnoses with offspring ASD", 
#        caption = "") +
#   guides(color = guide_legend(title = "ICD-10 Dx categories"), size = guide_legend(title = "Hazard ratio"))
# 
# 
# ggsave("Figures/Fig_01B_Model05_all.png", plot, width = 14, height = 7)
```

# Table S01 and S2 including Models 1, 2, 3, 4, and 5
```{r}
Model01_05_A <- Model01_05 %>% filter(a_c == "A") %>% left_join(table_asd_dx_A, by = "ICD10_3")
write_csv(Model01_05_A, "Tables/TabS01_Model01_05_A.csv")

Model01_05_C <- Model01_05 %>% filter(a_c == "C") %>% left_join(table_asd_dx_C, by = "ICD10_3")
write_csv(Model01_05_C, "Tables/TabS02_Model01_05_C.csv")
```


# Figure 02 comparing model 5 with model 11 by chronicity
```{r}
Model05.11$a_c <- as.factor(Model05.11$a_c) 
levels(Model05.11$a_c) <- c("Non-chronic", "Chronic")
dodger = position_dodge(width = 0.6)
plot <- ggplot(Model05.11, aes(y = HR, x = major, colour = model)) +
  geom_pointrange(aes(ymin = `2.5%`, ymax = `97.5%`),
                  position = dodger,
                  size = 0.6) +
  geom_hline(yintercept = 1.0, linetype = "dotted", linewidth = 0.7) +
  scale_y_log10(breaks = c( 0.50, 0.66, 1.00, 1.50, 2.00, 3.00),
                minor_breaks = NULL) +
  labs(y = "Hazard ratio", x = "ICD-10 level 3 diagnostic category") +
  coord_flip(ylim = c(0.48, 4.5)) + 
  theme_bw() + 
        scale_colour_manual(values=c('grey70', 'deepskyblue4'), labels = c("Single-diagnosis Model", "Multi-diagnosis Model")) + 
        theme(legend.position="bottom") + 
        #scale_shape_discrete(labels = c("Acute", "Chronic")) +
        guides(color = guide_legend(title = "Model")) +
  facet_wrap(~a_c, scales = "free_y", ncol = 1)
ggsave("Figures/Fig_02_Model11_05A.png", plot, width = 8, height = 11)
```

# Figure 02 comparing model 5 with model 11 (all together)
```{r}
dodger = position_dodge(width = 0.6)
plot <- ggplot(Model05.11, aes(y = HR, x = major, colour = model, shape = a_c)) +
  geom_pointrange(aes(ymin = `2.5%`, ymax = `97.5%`),
                  position = dodger,
                  size = 0.6) +
  geom_hline(yintercept = 1.0, linetype = "dotted", linewidth = 0.7) +
  scale_y_log10(breaks = c( 0.50, 0.66, 1.00, 1.50, 2.00, 3.00),
                minor_breaks = NULL) +
  labs(y = "Hazard ratio", x = "ICD-10 level 3 diagnostic category") +
  coord_flip(ylim = c(0.48, 4.5)) + 
  theme_bw() + 
        scale_colour_manual(values=c( 'grey75', rgb(0.15, 0.40, 0.50, 1.00)), labels = c("Multivariable Model", "Multi-diagnosis Model")) + 
        theme(legend.position="bottom") + 
        scale_shape_discrete(labels = c("Acute", "Chronic")) +
        guides(color = guide_legend(title = "Model"), shape = guide_legend(title = "Dx type"))
#ggsave("Figures/Fig_02_Model11_05.pdf", plot, width = 10, height = 9)
```

# Figure S01 Model 11 for ALL, Male, and Females
# We may consider droping "ALL" as it is always the weighted average of Male & Female, and in this between Male and Felame, closer to Male (as they account for ~ 75%+ of alal cases)
```{r}
Model11mf <-   Model11_s7f %>% 
  select(HR, `2.5%`, `97.5%`, ICD10_3, major, sub_chapter, chapter) %>% 
  mutate(model = "Female") %>%
  rbind(Model11_s7m %>% 
          select(HR, `2.5%`, `97.5%`, ICD10_3, major, sub_chapter, chapter) %>% 
          mutate(model = "Male")) %>% 
  left_join(a_c, by = "ICD10_3") %>% 
  left_join(select(table_prevalence, ICD10_3, prevalence, prevalence_pct), by = "ICD10_3") 


pct_labels <- Model11mf %>%
    arrange(major) %>% 
  distinct(major, .keep_all = T) 
pct_labels <-    print(pct_labels$ prevalence_pct)

Model11mf$major <- droplevels(Model11mf$major)

# Reorder levels of x based on y
Model11mf$prevalence_pct <- as.factor(Model11mf$prevalence_pct)

dodger = position_dodge(width = 0.6)

dodger = position_dodge(width = 0.6)
plot <- ggplot(Model11mf, aes(y = HR, x = major, colour = model)) +
  geom_pointrange(aes(ymin = `2.5%`, ymax = `97.5%`),
                  position = dodger,
                  size = 0.6) +
  geom_hline(yintercept = 1.0, linetype = "dotted", linewidth = 0.7) +
  scale_y_log10(breaks = c( 0.50, 0.66, 1.00, 1.50, 2.00, 3.00),
                minor_breaks = NULL) +
  labs(y = "Hazard ratio", x = "ICD-10 level 3 diagnostic category") +
  coord_flip(ylim = c(0.48, 4.5)) + 
  theme_bw() + 
        scale_colour_manual(values=c('deepskyblue4', 'grey70')) + 
        theme(legend.position="bottom") + 
        guides(color = guide_legend(title = "Model"), shape = guide_legend(title = "Dx type"))
ggsave("Figures/Fig_S01_Model11mf.png", plot, width = 8, height = 9)


plot <- ggplot(Model11mf, aes(y = HR, x = as.numeric(major), colour = model)) +
  geom_pointrange(aes(ymin = `2.5%`, ymax = `97.5%`),
                  position = dodger,
                  size = 0.6) +
  geom_hline(yintercept = 1.0, linetype = "dotted", linewidth = 0.7) +
  scale_y_log10(breaks = c( 0.50, 0.66, 1.00, 1.50, 2.00, 3.00),
                minor_breaks = NULL) +
  labs(y = "Hazard ratio", x = "ICD-10 level 3 diagnostic category") +
  scale_x_continuous(breaks = 1:n_distinct(Model11mf$major),
                     labels = levels(Model11mf$major),
                     sec.axis = sec_axis(~.,
                                         breaks = 1:n_distinct(Model11mf$major),
                                         labels = pct_labels,
                                         name = "Prevalence of ICD-10 level 3 diagnosis")) +
  coord_flip(ylim = c(0.48, 4.5)) + 
  theme_bw() + 
        scale_colour_manual(values=c('deepskyblue4', 'grey70')) + 
        theme(legend.position="bottom") + 
        guides(color = guide_legend(title = "Model"), shape = guide_legend(title = "Dx type"))
ggsave("Figures/Fig_S01_Model11mf_prv_pct.png", plot, width = 8, height = 9)
```

# Figure S02 Model 11 for ALL, ID, and no ID
# We may consider droping "ALL" as it is always the weighted average of Male & Female, and in this between Male and Felame, closer to Male (as they account for ~ 75%+ of alal cases)
```{r}
Model11idnid <-   Model11_s8id %>% 
        select(HR, `2.5%`, `97.5%`, ICD10_3, major, sub_chapter, chapter) %>% mutate(model = "ID") %>%
        rbind(Model11_s8nid %>% 
        select(HR, `2.5%`, `97.5%`, ICD10_3, major, sub_chapter, chapter) %>% 
                mutate(model = "no ID")) %>%
        left_join(a_c, by = "ICD10_3") %>% 
  left_join(select(table_prevalence, ICD10_3, prevalence, prevalence_pct), by = "ICD10_3") 


pct_labels <- Model11idnid %>%
    arrange(major) %>% 
  distinct(major, .keep_all = T) 
pct_labels <-    print(pct_labels$ prevalence_pct)

Model11idnid$major <- droplevels(Model11idnid$major)

# Reorder levels of x based on y
Model11idnid$prevalence_pct <- as.factor(Model11idnid$prevalence_pct)

dodger = position_dodge(width = 0.6)
plot <- ggplot(Model11idnid, aes(y = HR, x = major, colour = model)) +
  geom_pointrange(aes(ymin = `2.5%`, ymax = `97.5%`),
                  position = dodger,
                  size = 0.6) +
  geom_hline(yintercept = 1.0, linetype = "dotted", linewidth = 0.7) +
  scale_y_log10(breaks = c( 0.50, 0.66, 1.00, 1.50, 2.00, 3.00),
                minor_breaks = NULL) +
  labs(y = "Hazard ratio", x = "ICD-10 level 3 diagnostic category") +
  coord_flip(ylim = c(0.48, 4.5)) + 
  theme_bw() + 
        scale_colour_manual(values=c('grey70', 'deepskyblue4')) + 
        theme(legend.position="bottom") + 
        guides(color = guide_legend(title = "Model"), shape = guide_legend(title = "Dx type"))
ggsave("Figures/Fig_S02_Model11idnid.png", plot, width = 8, height = 9)


    
plot <- ggplot(Model11idnid, aes(y = HR, x = as.numeric(major), colour = model)) +
  geom_pointrange(aes(ymin = `2.5%`, ymax = `97.5%`),
                  position = dodger,
                  size = 0.6) +
  geom_hline(yintercept = 1.0, linetype = "dotted", linewidth = 0.7) +
  scale_y_log10(breaks = c( 0.50, 0.66, 1.00, 1.50, 2.00, 3.00),
                minor_breaks = NULL) +
  labs(y = "Hazard ratio", x = "ICD-10 level 3 diagnostic category") +
    scale_x_continuous(breaks = 1:n_distinct(Model11idnid$major),
                     labels = levels(Model11idnid$major),
                     sec.axis = sec_axis(~.,
                                         breaks = 1:n_distinct(Model11idnid$major),
                                         labels = pct_labels,
                                         name = "Prevalence of ICD-10 level 3 diagnosis")) +
  coord_flip(ylim = c(0.48, 4.5)) + 
  theme_bw() + 
        scale_colour_manual(values=c('grey70', 'deepskyblue4')) + 
        theme(legend.position="bottom") + 
        guides(color = guide_legend(title = "Model"), shape = guide_legend(title = "Dx type"))
ggsave("Figures/Fig_S02_Model11idnid_pct.png", plot, width = 8, height = 9)
```

```{r}
Model05.11$a_c <- as.factor(Model05.11$a_c) 
levels(Model05.11$a_c) <- c("Non-chronic", "Chronic")
dodger = position_dodge(width = 0.6)
plot <- ggplot(Model05.11, aes(y = HR, x = major, colour = model)) +
  geom_pointrange(aes(ymin = `2.5%`, ymax = `97.5%`),
                  position = dodger,
                  size = 0.6) +
  geom_hline(yintercept = 1.0, linetype = "dotted", linewidth = 0.7) +
  scale_y_log10(breaks = c( 0.50, 0.66, 1.00, 1.50, 2.00, 3.00),
                minor_breaks = NULL) +
  labs(y = "Hazard ratio", x = "ICD-10 level 3 diagnostic category") +
  coord_flip(ylim = c(0.48, 4.5)) + 
  theme_bw() + 
        scale_colour_manual(values=c( 'grey70', 'deepskyblue4'), labels = c("Multivariable Model", "Multi-diagnosis Model")) + 
        theme(legend.position="bottom") + 
        scale_shape_discrete(labels = c("Acute", "Chronic")) +
        guides(color = guide_legend(title = "Model"), shape = "none") +
  facet_wrap(~ a_c, scales = "free_y", ncol = 1)
ggsave("Figures/Fig_02_Model11_05.png", plot, width = 8, height = 11)
```


# Figure S04 Sibling and equivalent sample

```{r}
Modelref_vs_sib <-   Model20 %>% 
        select(HR, `2.5%`, `97.5%`, ICD10_3, major, sub_chapter, chapter) %>% mutate(model = "Reference Model (Sibling Sample)") %>%
        rbind(Model21_b %>% 
        select(HR, `2.5%`, `97.5%`, ICD10_3, major, sub_chapter, chapter) %>% 
                mutate(model = "Sibling Analysis")) %>%
        left_join(a_c, by = "ICD10_3")

Modelref_vs_sib$a_c <- as.factor(Modelref_vs_sib$a_c) 
levels(Modelref_vs_sib$a_c) <- c("Non-chronic", "Chronic")

dodger = position_dodge(width = 0.6)
plot <- ggplot(Modelref_vs_sib, aes(y = HR, x = major, colour = model)) +
  geom_pointrange(aes(ymin = `2.5%`, ymax = `97.5%`),
                  position = dodger,
                  size = 0.6) +
  geom_hline(yintercept = 1.0, linetype = "dotted", linewidth = 0.7) +
  scale_y_log10(breaks = c( 0.50, 0.66, 1.00, 1.50, 2.00, 3.00, 5.00),
                minor_breaks = NULL) +
  labs(y = "Hazard ratio", x = "ICD-10 level 3 diagnostic category") +
  coord_flip(ylim = c(0.48, 5.5)) + 
  theme_bw() + 
        scale_colour_manual(values=c( 'grey70', 'deepskyblue4')) + 
        theme(legend.position="bottom") + 
        guides(color = guide_legend(title = "Model"))  +
  facet_wrap(~a_c, scales = "free_y", ncol = 1)
ggsave("Figures/Fig_03_Modelsib_vs_refA.png", plot, width = 8, height = 11)
```

# Figure paternal/maternal comparing model 4
```{r}
dodger = position_dodge(width = 0.6)
plot <- ggplot(pat_mat_04, aes(y = HR, x = major, colour = p_m)) +
  geom_pointrange(aes(ymin = `2.5%`, ymax = `97.5%`),
                  position = dodger,
                  size = 0.6) +
  geom_hline(yintercept = 1.0, linetype = "dotted", linewidth = 0.7) +
  scale_y_log10(breaks = c( 0.50, 0.66, 1.00, 1.50, 2.00, 3.00),
                minor_breaks = NULL) +
  labs(y = "Hazard ratio", x = "ICD-10 level 3 diagnostic category") +
  coord_flip(ylim = c(0.48, 4.5)) + 
  theme_bw() + 
        scale_colour_manual(values=c('grey70', 'deepskyblue4'), labels = c("Paternal dx", "Maternal dx")) + 
        theme(legend.position="bottom") + 
        guides(color = guide_legend(title = "Type of diagnosis"), shape = FALSE)
ggsave("Figures/Fig_04_mat_patA.png", plot, width = 7, height = 6)
plot
```
```{r}
pat_mat_df <- pat_mat_04
pat_mat_df$HRc <- format(round(pat_mat_df$HR,2), nsmall = 2)
pat_mat_df$LL <- format(round(pat_mat_df$`2.5%`,2), nsmall = 2)
pat_mat_df$UL <- format(round(pat_mat_df$`97.5%`,2), nsmall = 2)
pat_mat_df$HR95 <- paste(pat_mat_df$HRc, (paste(pat_mat_df$LL, (paste(pat_mat_df$UL, "]", sep = "")), sep = ", ")), sep = " [")
pat_mat_df$sig <- ifelse(pat_mat_df$p < 0.05, "*", "")
pat_mat_df$sig <- ifelse(pat_mat_df$p  < 0.01, "**", pat_mat_df$sig)
pat_mat_df$sig <- ifelse(pat_mat_df$p  < 0.001, "***", pat_mat_df$sig)
pat_mat_df$HR95 <- paste(pat_mat_df$HR95, pat_mat_df$sig, sep ="")

pat_mat_df <- pat_mat_df %>% 
  select(ICD10_3, chapter, sub_chapter, major, HR95, p_m)
pat_df <- pat_mat_df %>% 
  filter(p_m == "d")
mat_df <- pat_mat_df %>% 
  filter(p_m == "m") %>% 
  select(ICD10_3, HR95) %>% rename(HR95_maternal = HR95)
pat_mat_df <- pat_df %>% 
  left_join(mat_df, by = "ICD10_3") %>% select(-p_m) %>% 
  left_join((Model05_S7 %>% 
               select(ICD10_3, HR95) %>% 
               rename(Model_05_S7 = HR95)), by = "ICD10_3")
write_csv(pat_mat_df, "Tables/TabS09_Pat_Mat.csv")
```


```{r}
Model11s1_s1red <- Model11_s1ref %>% 
        select(ICD10_3, HR95, chapter, sub_chapter, major) %>% 
        rename(M11_S1REF_HR95 = HR95) %>% 
        left_join((Model11_s1 %>% 
                           select(ICD10_3, HR95) %>% 
                           rename(M11_S1_HR95 = HR95)), by = "ICD10_3") %>% 
        left_join(a_c, by = "ICD10_3") %>% 
        select(ICD10_3, a_c, chapter, sub_chapter, major, M11_S1REF_HR95, M11_S1_HR95)
write_csv(Model11s1_s1red, "Tables/TabS06_Model11REF_S1.csv")

Model11_s2_s5 <- Model11 %>% 
        select(ICD10_3, HR95, chapter, sub_chapter, major) %>% 
        rename(M11REF_HR95 = HR95) %>% 
        left_join((Model11_s2 %>% 
                           select(ICD10_3, HR95) %>% 
                           rename(M11_S2_HR95 = HR95)), by = "ICD10_3") %>%
        left_join((Model11_s3 %>% 
                           select(ICD10_3, HR95) %>% 
                           rename(M11_S3_HR95 = HR95)), by = "ICD10_3") %>% 
        left_join((Model11_s4 %>% 
                           select(ICD10_3, HR95) %>% 
                           rename(M11_S4_HR95 = HR95)), by = "ICD10_3") %>% 
        left_join((Model11_s5 %>% 
                           select(ICD10_3, HR95) %>% 
                           rename(M11_S5_HR95 = HR95)), by = "ICD10_3") %>% 
        left_join(a_c, by = "ICD10_3") %>% 
        select(ICD10_3, a_c, chapter, sub_chapter, major, M11REF_HR95, M11_S2_HR95, M11_S3_HR95, M11_S4_HR95, M11_S5_HR95)
write_csv(Model11_s2_s5, "Tables/TabS07_Model11REF_S2_S5.csv")

Model11_T <-  Model11 %>% 
  left_join(table_asd_dx, by = "ICD10_3") %>% 
  left_join(a_c, by = "ICD10_3") %>%  
  select(ICD10_3, chapter, sub_chapter, major, HR95, ASD, No_ASD)
write_csv(Model11_T, "Tables/TabS05_Model11.csv")
```



```{r}
ModelsibREF_sib_sibm <- Model20 %>% 
        select(ICD10_3, HR95, chapter, sub_chapter, major) %>% 
        rename(M20_REF = HR95) %>% 
        left_join((Model21_b %>% 
                           select(ICD10_3, HR95) %>% 
                           rename(M_SIB = HR95)), by = "ICD10_3") %>%
        left_join((Model21_s6 %>% 
                           select(ICD10_3, HR95) %>% 
                           rename(M_SIB_M = HR95)), by = "ICD10_3") %>%
        left_join(a_c, by = "ICD10_3") %>% 
        select(ICD10_3, a_c, chapter, sub_chapter, major, M20_REF, M_SIB, M_SIB_M)
write_csv(ModelsibREF_sib_sibm, "Tables/TabS08_ModelSIB_SIBM.csv")
```


```{r}
ModelsibREF_sib_pchg <- Model20 %>% 
        left_join(Model21_b, by = "ICD10_3")

ModelsibREF_sib_pchg$pct1 <- paste0(round(((((ModelsibREF_sib_pchg$HR.y-1) - (ModelsibREF_sib_pchg$HR.x-1))  / (ModelsibREF_sib_pchg$HR.x-1))*100),1), "%")
ModelsibREF_sib_pchg$pct2 <- (((ModelsibREF_sib_pchg$HR.y-1) - (ModelsibREF_sib_pchg$HR.x-1))  / (ModelsibREF_sib_pchg$HR.x-1))*100
write_csv(ModelsibREF_sib_pchg, "Tables/TabS11_PCT_CHG.csv")

chg <- ModelsibREF_sib_pchg %>% 
  mutate(nul_op = case_when(pct2 < -100 ~ "Y",
                            TRUE ~ "N"),
         non_sig = case_when(sig.x == "" ~ "Y",
                             TRUE ~ "N"),
         group = case_when(pct2 > 0 ~ "Stronger",
                           TRUE ~ "Weaker"))

a <- chg %>% filter(nul_op == "N")
a1 <- chg %>% filter(nul_op == "N" & group == "Stronger")
a2 <- chg %>% filter(nul_op == "N" & group == "Weaker")
median(abs(a$pct2))
median(a1$pct2)
median(a2$pct2)
b <- chg %>% filter(nul_op == "N" & non_sig == "N")
b1 <- chg %>% filter(nul_op == "N" & non_sig == "N" & group == "Stronger")
b2 <- chg %>% filter(nul_op == "N" & non_sig == "N" & group == "Weaker")

median(abs(a$pct2))
median(a1$pct2)
median(a2$pct2)
median(abs(b$pct2))
median(b1$pct2)
median(b2$pct2)

median(abs(a$pct2[a$a_c.x == "A"]))
median(a1$pct2[a1$a_c.x == "A"])
median(a2$pct2[a2$a_c.x == "A"])
median(abs(b$pct2[b$a_c.x == "A"]))
median(b1$pct2[b1$a_c.x == "A"])
median(b2$pct2[b2$a_c.x == "A"])

median(abs(a$pct2[a$a_c.x == "C"]))
median(a1$pct2[a1$a_c.x == "C"])
median(a2$pct2[a2$a_c.x == "C"])
median(abs(b$pct2[b$a_c.x == "C"]))
median(b1$pct2[b1$a_c.x == "C"])
median(b2$pct2[b2$a_c.x == "C"])
```


```{r}
colnames(Model17) <- c("p-val", "HR", "2.5%", "97.5%", "Time")
ICD10_3 <- Model17$Time[seq(1, length(Model17$Time), 4)]
ICD10_3 <- rep(ICD10_3, each =4)
Model17 <- cbind(Model17, ICD10_3)
Model17$Time[Model17$Time == Model17$ICD10_3] <- "00-12"
Model17 <- left_join(Model17, ICD10, by = "ICD10_3")
```


```{r}
Model17$HR <- as.numeric(Model17$HR)
Model17$`2.5%` <- as.numeric(Model17$`2.5%`)
Model17$`97.5%` <- as.numeric(Model17$`97.5%`)
Model17$shape <- 0
Model17$shape[Model17$Time == "00-12"] <- 1
dodger = position_dodge(width = 0.8)
plot <- ggplot(Model17, aes(y = HR, x = major, colour = Time, shape = as.factor(shape))) +
  geom_pointrange(aes(ymin = `2.5%`, ymax = `97.5%`),
                  position = dodger,
                  size = 0.7) +
  geom_hline(yintercept = 1.0, linetype = "dotted", linewidth = 0.7) +
  scale_y_log10(breaks = c( 0.50, 0.66, 1.00, 1.50, 2.00, 3.00),
                minor_breaks = NULL) +
  labs(y = "Hazard ratio", x = "ICD-10 level 3 diagnostic category") +
  coord_flip(ylim = c(0.48, 4.5)) + 
  theme_bw() + 
        scale_colour_manual(values=c( 'dimgrey', "cadetblue4","lightcyan3", "lightcyan2")) + 
        theme(legend.position="bottom") + 
        guides(color = guide_legend(title = "Timing of dx"), shape = FALSE)
ggsave("Figures/Fig_03_Timing.pdf", plot, width = 8, height = 8)
```


```{r}
Model_all <- Model05_sig %>% 
  rename(model_4 = HR95) %>% 
  select(13, 14, 15, 16, 17, 11)

Model_11_t <- Model11 %>% 
  rename(model_11 = HR95) %>% 
  select(ICD10_3, model_11)

Model_20_t <- Model20 %>% 
  rename(model_sib_ref = HR95) %>% 
  select(ICD10_3, model_sib_ref)

Model_21b_t <- Model21_b %>% 
  rename(Model_sib = HR95) %>% 
  select(ICD10_3, Model_sib)

pat_mat_df_t <- pat_mat_df %>% 
  rename(Model_pat = HR95,
         Model_pat_ref_mat = HR95_maternal) %>% 
  select(ICD10_3, Model_pat, Model_pat_ref_mat)

Model_all <- Model_all %>% 
  left_join(Model_11_t, by = "ICD10_3")%>% 
  left_join(Model_20_t, by = "ICD10_3")%>% 
  left_join(Model_21b_t, by = "ICD10_3")%>% 
  left_join(pat_mat_df_t, by = "ICD10_3") %>% 
  mutate(m04_n = as.numeric(substr(model_4, 1, 4)) -1,
         m11_n = as.numeric(substr(model_11, 1, 4)) -1,
         sib_ref_n = as.numeric(substr(model_sib_ref, 1, 4)) -1,
         sib_n = as.numeric(substr(Model_sib, 1, 4)) -1,
         pat_m_ref_n = as.numeric(substr(Model_pat_ref_mat, 1, 4)) -1,
         pat_n = as.numeric(substr(Model_pat, 1, 4)) -1) %>% 
  mutate(m11_n_d = (m11_n - m04_n)/m04_n,
         sib_n_d = (sib_n - sib_ref_n)/sib_ref_n,
         pat_n_d = (pat_n - pat_m_ref_n)/pat_m_ref_n)
         
write_csv(Model_all, "Model_all.csv")
```

```{r}
pat_df <- pat_mat_04 %>% 
  filter(p_m == "d")
```

# Data for Overall Result Summary
```{r}
Model_all_sum <- Model05 %>% select(ICD10_3, a_c, major, HR, `p-val`) %>% 
  rename(p =  `p-val`) %>% 
  left_join((Model11 %>% 
               select(ICD10_3, HR, p_val) %>% 
               rename(HR_11 = HR,
                      p_11 = p_val)), by = "ICD10_3") %>%
  left_join((Model21_b %>%
               select(ICD10_3, HR, p_val) %>%
               rename(HR_sib = HR,
                      p_sib = p_val)), by = "ICD10_3") %>%
  left_join((pat_df %>% 
               select(ICD10_3, HR, p) %>% 
               rename(HR_pat= HR,
                      p_pat = p)), by = "ICD10_3") %>% 
  filter(!is.na(HR_11)) %>%  select(ICD10_3, a_c, major, HR, HR_11, HR_sib, HR_pat, p, p_11, p_sib, p_pat)

Model_all_sum$M11 <- ((Model_all_sum$HR_11-1) / (Model_all_sum$HR-1))
Model_all_sum$Msib <- ((Model_all_sum$HR_sib-1) / (Model_all_sum$HR-1))
Model_all_sum$Mpat <- ((Model_all_sum$HR_pat-1) / (Model_all_sum$HR-1))

Model_all_sum$M11_p <- ifelse(Model_all_sum$p_11 < 0.05, 1, 0)
Model_all_sum$Msib_p <- ifelse(Model_all_sum$p_sib < 0.05, 1, 0)
Model_all_sum$Mpat_p <- ifelse(Model_all_sum$p_pat < 0.05, 1, 0)

Model_all_sum$M11_cat <- ifelse((Model_all_sum$M11 < 0.6 | Model_all_sum$M11 > 1.4), 4, 3)
Model_all_sum$M11_cat <- ifelse((Model_all_sum$M11_cat == 3 & Model_all_sum$M11_p == 1), 1, Model_all_sum$M11_cat)
Model_all_sum$M11_cat <- ifelse((Model_all_sum$M11_cat == 4 & Model_all_sum$M11_p == 1), 2, Model_all_sum$M11_cat)
Model_all_sum$M11_cat <- ifelse(is.na(Model_all_sum$HR_11), NA, Model_all_sum$M11_cat)

Model_all_sum$Msib_cat <- ifelse((Model_all_sum$Msib < 0.6 | Model_all_sum$Msib > 1.4), 4, 3)
Model_all_sum$Msib_cat <- ifelse((Model_all_sum$Msib_cat == 3 & Model_all_sum$Msib_p == 1), 1, Model_all_sum$Msib_cat)
Model_all_sum$Msib_cat <- ifelse((Model_all_sum$Msib_cat == 4 & Model_all_sum$Msib_p == 1), 2, Model_all_sum$Msib_cat)
Model_all_sum$Msib_cat <- ifelse(is.na(Model_all_sum$HR_sib), NA, Model_all_sum$Msib_cat)

Model_all_sum$Mpat_cat <- ifelse((Model_all_sum$Mpat < 0.6 | Model_all_sum$Mpat > 1.4), 4, 3)
Model_all_sum$Mpat_cat <- ifelse((Model_all_sum$Mpat_cat == 3 & Model_all_sum$Mpat_p == 1), 1, Model_all_sum$Mpat_cat)
Model_all_sum$Mpat_cat <- ifelse((Model_all_sum$Mpat_cat == 4 & Model_all_sum$Mpat_p == 1), 2, Model_all_sum$Mpat_cat)
Model_all_sum$Mpat_cat <- ifelse(is.na(Model_all_sum$HR_pat), NA, Model_all_sum$Mpat_cat)

write_csv(Model_all_sum, "percent_change.csv")
Model_all_m5 <- Model_all_sum %>%
  mutate(Type = "Single-diagnosis Model (Reference)",
         Category = 1) %>% 
select(major, Type, Category, ICD10_3, a_c)

Model_all_m11 <- Model_all_sum %>%
  mutate(Type = "Multi-diagnosis Model",
         Category = M11_cat) %>% 
select(major, Type, Category, ICD10_3, a_c)

Model_all_msib <- Model_all_sum %>%
  mutate(Type = "Sibling Analysis",
         Category = Msib_cat) %>% 
select(major, Type, Category, ICD10_3, a_c)

Model_all_mpat <- Model_all_sum %>%
  mutate(Type = "Paternal Analysis",
         Category = Mpat_cat) %>% 
select(major, Type, Category, ICD10_3, a_c)

M_all_sum <- rbind(Model_all_m5, Model_all_m11, Model_all_msib, Model_all_mpat)
```

```{r}
model_category <- M_all_sum %>%
  arrange(ICD10_3, a_c) %>%               # sort your dataframe
  mutate(major = factor(major, unique(major)))
model_category$Type <- as.factor(model_category$Type)
levels(model_category$Type)
model_category$Type <- factor(model_category$Type, levels = c("Single-diagnosis Model (Reference)", "Multi-diagnosis Model", "Sibling Analysis", "Paternal Analysis"))
model_category$Category <- factor(model_category$Category, levels = c("1", "2", "3", "4"))

pdf("Figures/overall.pdf")
g1 <- ggplot(model_category, aes(x =  Type, major)) +
  geom_tile(aes(fill = as.factor(Category), width = 0.9, height =0.9)) +
  scale_fill_manual(values=c("dodgerblue3", "lightblue", "darkgoldenrod1", "firebrick3", "grey77"), drop=FALSE, labels = c("No/Minor change & significant", "Major change & significant", "No/Minor change & non-significant", "Major change & non-significant")) + 
  #geom_text(aes(label = P_cat), size = 2) +
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5, hjust=0))  + 
  labs(fill = "Effect of adjustment",y = element_blank(), x = element_blank()) + 
  theme(legend.position = "none") + 
  #coord_fixed(ratio = 0.4) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "white")) + scale_x_discrete(position = "top")
g1
dev.off()
pdf("Figures/overall_legend.pdf")
g1 <- ggplot(model_category, aes(x =  Type, major)) +
  geom_tile(aes(fill = as.factor(Category), width = 0.9, height =0.9)) +
  scale_fill_manual(values=c("dodgerblue3", "lightblue", "darkgoldenrod1", "firebrick3", "grey77"), drop=FALSE, labels = c("No/Minor change & significant", "Major change & significant", "No/Minor change & non-significant", "Major change & non-significant")) + 
  #geom_text(aes(label = P_cat), size = 2) +
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5, hjust=0))  + 
  labs(fill = "Effect of adjustment",y = element_blank(), x = element_blank()) + 
  #theme(legend.position = "none") + 
  coord_fixed(ratio = 0.7) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "white")) + scale_x_discrete(position = "top")
g1
dev.off()
```
# Data for Overall Result Summary with Matched References
```{r}
Model_all_sum <- Model05 %>% select(ICD10_3, a_c, major, HR, `p-val`) %>% 
  rename(p =  `p-val`) %>% 
  left_join((Model11 %>% 
               select(ICD10_3, HR, p_val) %>% 
               rename(HR_11 = HR,
                      p_11 = p_val)), by = "ICD10_3") %>%
  left_join((Model21_b %>%
               select(ICD10_3, HR, p_val) %>%
               rename(HR_sib = HR,
                      p_sib = p_val)), by = "ICD10_3") %>%
  left_join((Model20 %>%
               select(ICD10_3, HR, p_val) %>%
               rename(HR_sib_ref = HR,
                      p_sib_ref = p_val)), by = "ICD10_3") %>% 
  left_join((pat_df %>% 
               select(ICD10_3, HR, p) %>% 
               rename(HR_pat= HR,
                      p_pat = p)), by = "ICD10_3") %>%
  left_join((Model05_S7 %>% 
               select(ICD10_3, HR, `p-val`) %>% 
               rename(HR_pat_ref= HR,
                      p_pat_ref = `p-val`)), by = "ICD10_3") %>%
  filter(!is.na(HR_11)) %>%  select(ICD10_3, a_c, major, HR, HR_11, HR_sib, HR_sib_ref, HR_pat, HR_pat_ref, p, p_11, p_sib, p_sib_ref,  p_pat, p_pat_ref)

Model_all_sum$M11 <- ((Model_all_sum$HR_11-1) / (Model_all_sum$HR-1))
Model_all_sum$Msib <- ((Model_all_sum$HR_sib-1) / (Model_all_sum$HR_sib_ref-1))
Model_all_sum$Mpat <- ((Model_all_sum$HR_pat-1) / (Model_all_sum$HR_pat_ref-1))

Model_all_sum$M11_p <- ifelse(Model_all_sum$p_11 < 0.05, 1, 0)
Model_all_sum$Msib_p <- ifelse(Model_all_sum$p_sib < 0.05, 1, 0)
Model_all_sum$Mpat_p <- ifelse(Model_all_sum$p_pat < 0.05, 1, 0)

Model_all_sum$M11_cat <- ifelse((Model_all_sum$M11 < 0.6 | Model_all_sum$M11 > 1.4), 4, 3)
Model_all_sum$M11_cat <- ifelse((Model_all_sum$M11_cat == 3 & Model_all_sum$M11_p == 1), 1, Model_all_sum$M11_cat)
Model_all_sum$M11_cat <- ifelse((Model_all_sum$M11_cat == 4 & Model_all_sum$M11_p == 1), 2, Model_all_sum$M11_cat)
Model_all_sum$M11_cat <- ifelse(is.na(Model_all_sum$HR_11), NA, Model_all_sum$M11_cat)

Model_all_sum$Msib_cat <- ifelse((Model_all_sum$Msib < 0.6 | Model_all_sum$Msib > 1.4), 4, 3)
Model_all_sum$Msib_cat <- ifelse((Model_all_sum$Msib_cat == 3 & Model_all_sum$Msib_p == 1), 1, Model_all_sum$Msib_cat)
Model_all_sum$Msib_cat <- ifelse((Model_all_sum$Msib_cat == 4 & Model_all_sum$Msib_p == 1), 2, Model_all_sum$Msib_cat)
Model_all_sum$Msib_cat <- ifelse(is.na(Model_all_sum$HR_sib), NA, Model_all_sum$Msib_cat)

Model_all_sum$Mpat_cat <- ifelse((Model_all_sum$Mpat < 0.6 | Model_all_sum$Mpat > 1.4), 4, 3)
Model_all_sum$Mpat_cat <- ifelse((Model_all_sum$Mpat_cat == 3 & Model_all_sum$Mpat_p == 1), 1, Model_all_sum$Mpat_cat)
Model_all_sum$Mpat_cat <- ifelse((Model_all_sum$Mpat_cat == 4 & Model_all_sum$Mpat_p == 1), 2, Model_all_sum$Mpat_cat)
Model_all_sum$Mpat_cat <- ifelse(is.na(Model_all_sum$HR_pat), NA, Model_all_sum$Mpat_cat)

write_csv(Model_all_sum, "percent_change.csv")
Model_all_m5 <- Model_all_sum %>%
  mutate(Type = "Single-diagnosis Model (Reference)",
         Category = 1) %>% 
select(major, Type, Category, ICD10_3, a_c)

Model_all_m11 <- Model_all_sum %>%
  mutate(Type = "Multi-diagnosis Model",
         Category = M11_cat) %>% 
select(major, Type, Category, ICD10_3, a_c)

Model_all_msib <- Model_all_sum %>%
  mutate(Type = "Sibling Analysis",
         Category = Msib_cat) %>% 
select(major, Type, Category, ICD10_3, a_c)

Model_all_mpat <- Model_all_sum %>%
  mutate(Type = "Paternal Analysis",
         Category = Mpat_cat) %>% 
select(major, Type, Category, ICD10_3, a_c)

M_all_sum <- rbind(Model_all_m5, Model_all_m11, Model_all_msib, Model_all_mpat)
```

```{r}
model_category <- M_all_sum %>%
  arrange(ICD10_3, a_c) %>%               # sort your dataframe
  mutate(major = factor(major, unique(major)))
model_category$Type <- as.factor(model_category$Type)
levels(model_category$Type)
model_category$Type <- factor(model_category$Type, levels = c("Single-diagnosis Model (Reference)", "Multi-diagnosis Model", "Sibling Analysis", "Paternal Analysis"))
model_category$Category <- factor(model_category$Category, levels = c("1", "2", "3", "4"))

pdf("Figures/overall_corrected.pdf")
g1 <- ggplot(model_category, aes(x =  Type, major)) +
  geom_tile(aes(fill = as.factor(Category), width = 0.9, height =0.9)) +
  scale_fill_manual(values=c("dodgerblue3", "lightblue", "darkgoldenrod1", "firebrick3", "grey77"), drop=FALSE, labels = c("No/Minor change & significant", "Major change & significant", "No/Minor change & non-significant", "Major change & non-significant")) + 
  #geom_text(aes(label = P_cat), size = 2) +
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5, hjust=0))  + 
  labs(fill = "Effect of adjustment",y = element_blank(), x = element_blank()) + 
  theme(legend.position = "none") + 
  #coord_fixed(ratio = 0.4) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "white")) + scale_x_discrete(position = "top")
g1
dev.off()
pdf("Figures/overall_legend_corrected.pdf")
g1 <- ggplot(model_category, aes(x =  Type, major)) +
  geom_tile(aes(fill = as.factor(Category), width = 0.9, height =0.9)) +
  scale_fill_manual(values=c("dodgerblue3", "lightblue", "darkgoldenrod1", "firebrick3", "grey77"), drop=FALSE, labels = c("No/Minor change & significant", "Major change & significant", "No/Minor change & non-significant", "Major change & non-significant")) + 
  #geom_text(aes(label = P_cat), size = 2) +
  theme(axis.text.x = element_text(angle = 60, vjust = 0.5, hjust=0))  + 
  labs(fill = "Effect of adjustment",y = element_blank(), x = element_blank()) + 
  #theme(legend.position = "none") + 
  coord_fixed(ratio = 0.7) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "white")) + scale_x_discrete(position = "top")
ggsave("Figures/Fig_05_Overall.png", g1, width = 7, height = 8)
g1
dev.off()
```

```{r}
# model_category <- read_csv(file_path <- "/Users/vk/Library/CloudStorage/OneDrive-Personal/Documents/Mount Sinai/-Projects/4. M_dx_R01/Data/model_category.csv")
# model_category$Category [model_category$Type == "Multivariable Model (Reference)"] <- 1
# library(dplyr)
# model_category <- model_category %>%
#   arrange(ICD10_3, a_c) %>%               # sort your dataframe
#   mutate(major = factor(major, unique(major)))
# model_category$Type <- as.factor(model_category$Type)
# levels(model_category$Type)
# model_category$Type <- factor(model_category$Type, levels = c("Multivariable Model (Reference)", "Multi-diagnosis Model", "Sibling Analysis", "Paternal Analysis"))
# model_category$Category <- factor(model_category$Category, levels = c("1", "3", "2", "4"))
# 
# pdf("Figures/overall.pdf")
# g1 <- ggplot(model_category, aes(x =  Type, major)) +
#   geom_tile(aes(fill = as.factor(Category), width = 0.9, height =0.9)) +
#   scale_fill_manual(values=c("dodgerblue3", "lightblue", "darkgoldenrod1", "firebrick3", "grey77"), drop=FALSE, labels = c("No/Minor change & significant", "Major change & significant", "No/Minor change & non-significant", "Major change & non-significant")) + 
#   #geom_text(aes(label = P_cat), size = 2) +
#   theme(axis.text.x = element_text(angle = 60, vjust = 0.5, hjust=0))  + 
#   labs(fill = "Effect of adjustment",y = element_blank(), x = element_blank()) + 
#   theme(legend.position = "none") + 
#   #coord_fixed(ratio = 0.4) + 
#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
# panel.background = element_blank(), axis.line = element_line(colour = "white")) + scale_x_discrete(position = "top")
# g1
# dev.off()
# pdf("Figures/overall_legend.pdf")
# g1 <- ggplot(model_category, aes(x =  Type, major)) +
#   geom_tile(aes(fill = as.factor(Category), width = 0.9, height =0.9)) +
#   scale_fill_manual(values=c("dodgerblue3", "lightblue", "darkgoldenrod1", "firebrick3", "grey77"), drop=FALSE, labels = c("No/Minor change & significant", "Major change & significant", "No/Minor change & non-significant", "Major change & non-significant")) + 
#   #geom_text(aes(label = P_cat), size = 2) +
#   theme(axis.text.x = element_text(angle = 60, vjust = 0.5, hjust=0))  + 
#   labs(fill = "Effect of adjustment",y = element_blank(), x = element_blank()) + 
#   #theme(legend.position = "none") + 
#   coord_fixed(ratio = 0.7) + 
#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
# panel.background = element_blank(), axis.line = element_line(colour = "white")) + scale_x_discrete(position = "top")
# g1
# dev.off()
```


```{r}
scale_fill_manual(values=c("#053061", "#2166AC", "#4393C3", "#92C5DE", "#D1E5F0", "#F7F7F7", "#FDDBC7", "#F4A582", "#D6604D", "#B2182B", "#67001F", "grey77"), drop=FALSE) +
  
  
# Create a sample dataframe with two categorical variables
data <- data.frame(
  Category = rep(c("A", "B", "C"), each = 3),
  Variable1 = rep(c("Low", "Medium", "High"), times = 3),
  Variable2 = rep(c("CategoryX", "CategoryY", "CategoryZ"), each = 3)
)

# Create a ggplot
gg <- ggplot(data, aes(x = Category)) +
  geom_bar(aes(y = Variable1, fill = Variable1), stat = "identity") +
  theme_minimal()

# Get the y-axis range for both sides
y_range <- range(data$Variable1, data$Variable2)

# Add labels on both sides of the y-axis
gg + annotation_custom(
  grid::textGrob("Variable1", rot = 0, vjust = 1, gp = gpar(col = "black")),
  xmin = -Inf, xmax = Inf, ymin = y_range[1], ymax = y_range[2]
) +
annotation_custom(
  grid::textGrob("Variable2", rot = 0, vjust = 1, gp = gpar(col = "red")),
  xmin = -Inf, xmax = Inf, ymin = y_range[1], ymax = y_range[2]
) +
scale_fill_manual(values = c("blue", "green", "orange")) +
scale_y_discrete(sec.axis = sec_axis(~., name = "Variable2"))
```
```{r}
SE_Model11 <- Model11 %>% 
  mutate(L_HR = log(exp.coef.),
         LIM = log(upper..95) - L_HR) %>% 
  mutate(SE = LIM/1.959964,
         increase = ((abs(L_HR) - LIM)/LIM)* 100)

SE_Model05 <- Model05 %>% 
  mutate(L_HR = log(HR),
         LIM = log(`97.5%`) - L_HR) %>% 
  mutate(SE = LIM/1.959964,
         increase = ((abs(L_HR) - LIM)/LIM)* 100)

write_csv(SE_Model05, "Tables/TabS05_SE_Change.csv")
```
```{r}
acute <- c(0.145, 0.184, 0.267, 0.354, 0.382, 0.473, 0.574, 0.611, 0.836, 0.884, 0.888, 1.07, 1.139, 1.356, 1.448, 1.565, 2.051, 6.831)
summary(acute)
chronic <- c(0.069, 0.497, 0.518, 0.661, 0.702, 0.76, 0.808, 0.847, 0.875, 0.947, 1.008, 1.031, 1.043, 1.3, 1.385, 1.492, 1.709, 1.977, 2.618, 2.691)
summary(chronic)

chg <- read_csv("Tables/TabS11_PCT_CHG.csv") %>% 
  mutate(nul_op = case_when(pct3 == "Null/opposite direction" ~ "Y",
                            TRUE ~ "N"),
         non_sig = case_when(is.na(sig.x) ~ "Y",
                             TRUE ~ "N"),
         group = case_when(pct2 > 0 ~ "Stronger",
                           TRUE ~ "Weaker"))

a <- chg %>% filter(nul_op == "N")
a1 <- chg %>% filter(nul_op == "N" & group == "Stronger")
a2 <- chg %>% filter(nul_op == "N" & group == "Weaker")
median(abs(a$pct2))
median(a1$pct2)
median(a2$pct2)
b <- chg %>% filter(nul_op == "N" & non_sig == "N")
b1 <- chg %>% filter(nul_op == "N" & non_sig == "N" & group == "Stronger")
b2 <- chg %>% filter(nul_op == "N" & non_sig == "N" & group == "Weaker")
median(abs(b$pct2))
median(b1$pct2)
median(b2$pct2)
 test <- M_all_sum %>% left_join(chg, by = "ICD10_3") %>% filter(Type == "Sibling Analysis") %>%  mutate(abs_pct = abs(pct2))
```

